%%%%% Appendix: Computational and Empirical Details %%%%%
%
% Scope:
%   - Appendix A: Computing the Bundle (referenced from Section 5.1)
%   - Appendix B: User Study Protocol (referenced from Sections 7.1, 7.2)
%
% Structure:
%   - A and B are top-level sections.
%   - B is composed of four \paragraph blocks
%     (Participants / Task and Procedure / Behavioral Metrics / Questionnaire);
%     only B as a whole is referenced from the main text, so the inner
%     subdivisions do not need their own labels.
%
% Word budget:
%   - Appendix A: ~180 words
%   - Appendix B: ~465 words  (Participants 65 / Task & Proc. 150
%                              / Metrics 200 / Questionnaire 50)
%   - Total:      ~645 words
%
% Note: \appendix is declared in main.tex before \input{appendix.tex}.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Appendix A: Computing the Bundle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Computing the Bundle}\label{app:algorithm}

The objective in Eq.~\eqref{eq:objective} is not directly tractable.
We treat the problem as one of unbalanced optimal transport, in which
the two directions $p \to q$ and $q \to p$ are addressed separately.

In the $q \to p$ direction, with the genre-ness coordinates
$U = \{u_k\}_{k=1}^K$ and the atmosphere coordinates
$V = \{v_n\}_{n=1}^N$ held fixed, the optimum over the embedding
$\Phi$ admits a closed form:
\begin{equation}\label{eq:phi-closed}
    \Phi(u, v \mid U, V) =
    \frac{\sum_k \mathcal{N}(u \mid u_k, \alpha^{-1} I)\, \varphi_k(v)}
    {\sum_l \mathcal{N}(u \mid u_l, \alpha^{-1} I)},
\end{equation}
where $\varphi_k$ is the manifold model of the $k$-th genre:
\begin{equation}\label{eq:varphi}
    \varphi_k(v) =
    \frac{\sum_{n:\rho_{kn}=1} \mathcal{N}(v \mid v_n, \alpha^{-1} I)\, \mathbf{x}_n}
    {\sum_{m:\rho_{km}=1} \mathcal{N}(v \mid v_m, \alpha^{-1} I)}.
\end{equation}
Here $\rho_{kn} = 1$ when item $n$ belongs to genre $k$ and $0$
otherwise, and $\alpha$ controls the kernel width.

Substituting this expression back into the $p \to q$ direction reduces
the joint problem to one over $U$ and $V$ alone:
\begin{equation}\label{eq:E-UV}
    E[U, V] = \sum_n p(n) \left\{
    \tfrac{\beta}{2}
    \bigl\|\mathbf{x}_n - \Phi(u_{c_n}, v_n \mid U, V)\bigr\|^2
    - \log q(u_{c_n}) - \log q(v_n)
    \right\},
\end{equation}
where $c_n$ is the genre label of item $n$ (as in
Section~\ref{sec:modeling}), and $\beta$ weighs the reconstruction term
against the density terms. Here $p(n)$ denotes the data probability of item $n$, and $q(u)$, $q(v)$ its marginal model distributions. We minimize $E[U, V]$ by stochastic gradient
Langevin dynamics.

The derivation, theoretical properties, and convergence analysis of this method
are developed separately, as a self-contained study in disentanglement learning
theory.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Appendix B: User Study Protocol
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{User Study Protocol}\label{app:user_study}

% --- 目的 -----------------------------------------------------------
% 本文 Section 7.1 (全体) と Section 7.2 (metrics 定義) からの参照先。
% Reviewer の「user study 方法論の記述不足」懸念への直接応答。
% 本文の Section 7 は「観察モード」で書くため、「何を見たか」を本文に、
% 「どう測ったか」をここに置く役割分担。
%
% --- 構成 (4 paragraphs) -------------------------------------------
%   \paragraph{Participants.}        ~ 65 words
%   \paragraph{Task and Procedure.}  ~150 words
%   \paragraph{Behavioral Metrics.}  ~200 words
%   \paragraph{Questionnaire.}       ~ 50 words


\paragraph{Participants.}
We recruited 135 participants across two independent experiments.
Experiment~1 involved 63 participants (Group~CP: $n=31$, Group~PC: $n=32$;
ages~18--43, mean~21.6, median~20; 46~male, 17~female).
Experiment~2 involved 72 participants (ages~21--62, mean~30.2, median~25;
55~male, 17~female).
Participants were recruited through open calls.


\paragraph{Task and Procedure.}
Participants explored the music map and created a playlist titled
\textit{`Fresh Finds'}, marking playlist candidates with $\star$ and
personal favorites with $\heartsuit$. Instructions emphasized natural
behavior: ``Please explore music as you normally would. This is not
a competition for playlist size, but an observation of your usual
discovery process.'' Each session began with a short tutorial in which
participants learned basic operations (genre selection, map navigation,
playback, and marking) using songs excluded from the main trials. They
then performed the experimental sequences described in
Section~\ref{sec:experiments}, followed by a questionnaire and a brief
interview. The 2,500-song dataset was partitioned into two disjoint
subsets so that no song appeared in both system~P and systems~C1/C2.
All sessions were conducted on 27-inch monitors with a standard mouse.


\paragraph{Behavioral Metrics.}
We used three quantitative indicators of exploratory behavior.
(1)~\textit{Genre entropy} $H_g = -\sum_k p_k \log p_k$ measured breadth
across 10~genres, where $p_k$ denotes the proportion of items
in genre~$k$.
(2)~\textit{Atmosphere entropy} $H_a$ measured diversity within the
2D~atmosphere space~$\mathcal{V}$, discretized into a $20 \times 20$ grid
with kernel density estimation. Because system~C1 represents each genre
on an independent manifold and admits no unified atmosphere space, $H_a$
for C1 was computed as the weighted average of genre-conditional
entropies. For systems~P and~C2, which share a unified atmosphere space,
$H_a$ was computed over that space; in C2 this measures entropy over
the \textit{true underlying distribution} that the interface conceals
from users, so $H_a$ in~C2 captures whether users move along
correspondences they cannot directly see.
(3)~\textit{Exploration chain length} quantified consecutive
Focus-of-Interest (FoI) movements within atmosphere distance $d = 0.28$.
In system~P, chains could continue across genre boundaries; in C1/C2,
genre switches terminated chains.
Significance was evaluated using paired $t$-tests and Wilcoxon
signed-rank tests with Bonferroni correction.


\paragraph{Questionnaire.}
Participants rated each system on 20~items using a 5-point Likert scale
(1~=~strongly disagree, 5~=~strongly agree). Items were grouped into
six aspects: (A)~Ease of discovery, (B)~Leads to the unexpected,
(C)~Trigger-rich, (D)~Highlights triggers, (E)~Enables connections,
and (F)~Discovering preferences. Aspects~B--E were adapted from
McCay-Peet and Toms~\cite{McCayPeet20181}; A and F were developed for
this study. The complete list of items is provided in
Supplement~\ref{sup:questionnaire}.




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% End of Appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
