\documentclass[11pt,a4paper]{article}

% ===== Packages =====
\PassOptionsToPackage{numbers,sort&compress}{natbib}

\usepackage[T1]{fontenc}
\usepackage{newtxtext,newtxmath}
\usepackage{amsmath,amsfonts,bm}
\usepackage{graphicx}
\usepackage{booktabs,multirow,array}
\usepackage{caption,subcaption}
\usepackage{algorithm2e}
\usepackage{relsize}
\usepackage[margin=2.5cm]{geometry}
\usepackage{setspace}
\usepackage[dvipsnames]{xcolor}
\usepackage[hyphens]{url}
\usepackage{natbib}  
\usepackage{comment}

% ===== External References =====
\usepackage{xr}
\externaldocument{supplements}

% ===== Proposition Environment =====
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{proof}{Proof}
\newtheorem{hypothesis}{Hypothesis}

\DeclareMathOperator*{\argmin}{arg\,min}

\renewcommand{\topfraction}{0.75}  
\renewcommand{\bottomfraction}{0.75} 
\renewcommand{\textfraction}{0.2} 

\begin{document}

% ===== Title and Authors =====
\title{Through Alice's Rabbit Holes: \\
    A Disentangled Tale of Serendipity Paradoxes}
\author{
    Tatsuya Kanatsu\textsuperscript{1}, Tohru Iwasaki\textsuperscript{2}, Hideaki Ishibashi\textsuperscript{1}, \\
    Kaori Yoshida\textsuperscript{1}, and Tetsuo Furukawa\textsuperscript{1} \\[3pt]
    \small \textsuperscript{1}Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Japan \\
    \small \textsuperscript{2}Data / AI System Division, ZOZO, Inc., Japan \\
    \small Corresponding author: furukawa@brain.kyutech.ac.jp
}
\date{}
\author{} % Remove the author name from the title page
\maketitle

\begin{abstract}\noindent
    Serendipity is often described as finding something ``unexpected yet relevant.''
    We read this as the \textit{distant-yet-close paradox}: items explicitly distant
    in named features yet implicitly close in unnamed ones. This is a problem of
    \textit{representation}, not of interface design: the paradox can be addressed
    only in a space that disentangles the two senses of closeness. Disentangled
    representation, however, is ill-posed; the right one is singled out by an
    \textit{inductive bias} declaring what one wants. We propose \textit{optimal
        transport} as that bias, and the representation it yields is the
    \textbf{Optimal Transport Fiber Bundle (OT-FB)}: genre-ness and atmosphere
    coordinates form separable axes of one geometry, connected by \textit{rabbit
        holes} between genre-distant yet atmosphere-close regions. Two
    views render this one structure: the \textbf{multi-galaxy curved universe}, the
    entangled form in which data arrive, and the \textbf{multi-floor library}, the
    disentangled form in which users may walk. Mathematics secures the concept:
    once declared, the bundle is well-defined and essentially unique. Computation
    gives it reality: the bundle is learned from real data and offered to the
    reader as an explorable system. The unnamed is never put into words; held as
    geometry, it gains a place where it can be felt. The contribution is the
    disentangled representation itself: distant yet close ceases to be a paradox
    and becomes the local geometry of the bundle.
\end{abstract}

\begin{quote}\parindent=0pt\parskip=.5em\noindent
    \begin{center}
        \textbf{Structured Abstract}
    \end{center}
    \textbf{Purpose.}
    We address the \textit{distant-yet-close paradox} of serendipity---items
    explicitly distant in named features yet implicitly close in unnamed
    ones---as a problem of \textit{information representation} rather than
    interface design. Our aim is to construct, from data, a \textit{disentangled
        representation space} in which this paradox becomes navigable.

    \textbf{Design/methodology/approach.}
    Disentangled representation is ill-posed; the right one is singled out by an
    \textit{inductive bias} declaring what one wants. We propose the
    \textit{optimal transport (OT) hypothesis} as that bias, aligning the
    atmosphere coordinate across genres. Under this hypothesis the
    representation takes the form of an \textbf{Optimal Transport Fiber Bundle
        (OT-FB)}, in which genre-ness and atmosphere coordinates form separable
    axes of one geometry, connected by \textit{rabbit holes}. The paper is
    self-contained at three levels: \textbf{conceptual} (the multi-galaxy curved
    universe and the multi-floor library), \textbf{mathematical}
    (well-definedness and essential uniqueness of the bundle), and
    \textbf{computational} (an alternating optimization that learns the bundle
    from data).

    \textbf{Findings.}
    In the OT-FB learned from the Million Song Dataset, the atmosphere
    coordinate emerged common to all ten genres yet independent of any: tags
    that cross genre boundaries organized the atmosphere space, while
    genre-bound tags did not. Quantitative comparison with baseline methods
    supports this separation. The learned representation is offered to the
    reader as an explorable system.

    \textbf{Originality/value.}
    The contribution is the disentangled representation itself, given
    well-defined mathematical form by the OT hypothesis and shown to be
    learnable from real data. It offers an account of why the felt closeness of
    serendipity resists reduction to named attributes, and of what a
    representation must hold instead. With this representation in place, distant
    yet close ceases to be a paradox and becomes the local geometry of the bundle.
\end{quote}

\noindent\textbf{Keywords:}
serendipity, exploratory search, information representation,
disentangled representation, optimal transport, fiber bundle


\input{sec1.tex}
\input{sec2.tex}
\input{sec3.tex}
\input{sec4.tex}
\input{sec5.tex}
\input{sec6.tex}
\input{sec7.tex}
\input{sec8.tex}

\begin{comment}
\section*{Acknowledgments}
This research was supported in part by JSPS KAKENHI Grant Number 21K12061. We also gratefully acknowledge the support of Zozo, Inc. We are deeply grateful to Ms.\ Hirowatari for her invaluable assistance. The music data used in this study was utilized in accordance with YouTube's terms of service, based on content from YouTube Music.
\end{comment}

\bibliographystyle{IEEEtran}
\bibliography{ref}

\appendix
\input{appendix.tex}

\end{document}




