%%%%% Section 5. Learning the Bundle from Data %%%%%
\section{Learning the Bundle from Data}\label{sec:computational}

Section~\ref{sec:modeling} gave OT-FB its mathematical form. We carry
it now to the \textbf{third of the five levels---the Computational}:
learning the bundle from real data.


%%% Subsection 5.1 Computing the bundle from data %%%
\subsection{Computing the bundle from data}\label{subsec:OTFB-computation}

With the conceptual structure in place, we now turn to the computational
task: given a dataset, how do we learn the OT-FB? From the genre labels and
body data $\{(c_n, \mathbf{x}_n)\}$ we must recover the atmosphere
coordinate $v_n$ of each item, the genre-ness coordinate $u_k$ of each
genre, and the generating map $\Phi(u, v)$ embedding the library
into the universe.

Learning the OT-FB amounts to finding the embedding $\Phi$ that
minimizes the optimal-transport cost between the empirical data
distribution $p_\text{data}$ and the model distribution $q_\Phi$:
\begin{equation}\label{eq:objective}
    \Phi^* = \arg\min_\Phi \left[
        \inf_{\gamma \in \Pi(p_\text{data}, q_\Phi)}
        \iint \|\mathbf{x} - \mathbf{x}'\|^2 \,
        \gamma(\mathbf{x}, \mathbf{x}') \, d\mathbf{x} \, d\mathbf{x}'
        \right],
\end{equation}
where $\gamma$ is a transport plan.

Solving this objective from data is not a routine exercise. The combined
task---disentangled representation
learning~\cite{Locatello20197247} and the alignment of distributions
across multiple manifolds~\cite{peyre2019computational}---is
notoriously difficult under unsupervised conditions. We have developed a
dedicated optimization algorithm, presented in
Appendix~\ref{app:algorithm}.

This method admits two further extensions. First, when an item carries a soft
genre distribution---\textit{Harry Potter} as fantasy and school story,
Gershwin's works as jazz and classical---the hard label $c_n$ is replaced by
that distribution, and $u_{c_n}$ becomes a per-item coordinate $u_n$---genre-ness
made continuous, item by item. Second, when
richer descriptors are available---artist, era, and others---the genre-ness
space $\mathcal{U}$ can itself be further disentangled into independent axes:
genre-ness, artist-ness, age-ness, and so on---a catalog's facets, made
continuous. Atmosphere stays the remainder of them all.


