%%%%% Section 8. Discussion %%%%%
\section{Discussion}\label{sec:discussion}

Our point of departure was the \textit{distant-yet-close paradox} of
serendipity. The pursuit led us to the need for a well-formed
information representation space---one in which an \textbf{atmospheric
axis}, swept with a genre held fixed, and a \textbf{genre-ness axis},
swept with an atmosphere held fixed, are disentangled. We modeled such
a space as the multi-floor library.

Learning such a representation from data confronts a hard problem:
straightening the galaxies of a curved universe with no
\textit{a priori} knowledge of how a star in one galaxy relates to a
star in another. This is nothing other than the task of defining, in
mathematical form, an inductive bias that matches what we want.

We therefore asked ourselves what kind of information representation
space we wanted, and put the answer in well-defined form. The answer
was the OT hypothesis. Under it, the disentangled representation we
sought---the multi-floor library---took the form of an OT-FB.

Computing an OT-FB from data was itself no small undertaking; we
developed a method that does so. With it, we built a web application
in which the representation itself serves as the interface---a virtual
library with rabbit holes---requiring no special UI craft.

We then observed how users behaved and what they experienced inside
this library. They paused at places that resonated with what they
were seeking, moved between floors through the rabbit holes, and
found what they were looking for. Along the way, they discovered not
only items they liked, but a sense of what their preferences were.

Through all of this, what is it that we have come to understand?

\paragraph{The space had to be disentangled.}
In an entangled space, distance and closeness fold into each other:
items may be far in one sense and near in another, but the sense in
which they are far or near is not separately readable. The paradox of
\textit{distant yet close} cannot even be stated there. The
disentangled space is not one design choice among others; it is the
precondition for the paradox to be addressable at all.

\paragraph{An inductive bias was needed, and OT was a fitting one.}
Statistical independence alone does not pin down what is independent
from what; the same data admit many disentanglings. The real task is
to ask what unnamed commonality we tacitly expect across genres, and
to give it a definite mathematical form. The OT hypothesis is one such
form, simple and domain-agnostic: along the rabbit holes, the mass of
one genre is transported to another at minimum cost. Other forms are
possible, none can be shown superior to another---yet a form this
general and reasonable is not easy to find.

\paragraph{What this hypothesis still allows.}
The hypothesis admits more than one axis. On the descriptor side,
attributes beyond genre---artist, era, and the like---each layer in
their own descriptor-ness axis. On the body side, an item may be
embedded through several views, each carving out its own universe with
its own rabbit hole. Our children's
literature instantiation does exactly this: from the same books, the
noun tags and the adjective tags give two descriptions, hence two body
data, carrying a \textbf{thematic atmosphere} and a \textbf{tonal
atmosphere} respectively, disentangled through the same
shelves.\footnote{Available at
    \url{https://serendipity-books-demo.vercel.app/?lang=en}.} However
many axes are added, they remain disentangled as far as the OT
hypothesis allows.
