\documentclass[11pt,a4paper]{article}

% ===== パッケージ =====
\PassOptionsToPackage{numbers,sort&compress}{natbib}

\usepackage[T1]{fontenc}
\usepackage{newtxtext,newtxmath}
\usepackage{amsmath,amsfonts,bm}
\usepackage{graphicx}
\usepackage{booktabs,multirow,array}
\usepackage{caption,subcaption}
\usepackage{algorithm2e}
\usepackage{relsize}
\usepackage[margin=2.5cm]{geometry}
\usepackage{setspace}
\usepackage[dvipsnames]{xcolor}
\usepackage[hyphens]{url}
\usepackage{natbib}  
\usepackage{multirow}

% ===== External References =====
\usepackage{xr}
\externaldocument{main}

% ===== Proposition Environment =====
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{proof}{Proof}

\DeclareMathOperator*{\argmin}{arg\,min}

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\theequation}{S\arabic{equation}}

\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\topfraction}{0.8}     % ページ上部に float を詰める割合を緩める
\renewcommand{\bottomfraction}{0.8}  % ページ下部も少し緩める
\renewcommand{\textfraction}{0.2}   % テキストの最低割合を下げる

\begin{document}

% ===== Title and Authors =====
\title{Supplementary Materials for \\
    ``Through Alice's Rabbit Holes: \\
    A Disentangled Tale of Serendipity Paradoxes''}
\author{
    Tatsuya Kanatsu\textsuperscript{1}, Tohru Iwasaki\textsuperscript{2}, Hideaki Ishibashi\textsuperscript{1}, \\
    Kaori Yoshida\textsuperscript{1}, and Tetsuo Furukawa\textsuperscript{1} \\[3pt]
    \small \textsuperscript{1}Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Japan \\
    \small \textsuperscript{2}Data / AI System Division, ZOZO, Inc., Japan \\
    \small Corresponding author: furukawa@brain.kyutech.ac.jp
}
\date{}
\maketitle

\section{Ethics}
The study protocol was approved by the Research Ethics Committee
for Research Involving Human Subjects, Graduate School of Life
Science and Systems Engineering, Kyushu Institute of Technology
(Approval No. 25-7).

All participants received written and oral explanations of the
study's purpose, procedures, and data handling, and provided
written informed consent prior to participation.



\section{Use of Large Language Models}\label{sup:use_of_llms}
In preparing this manuscript and the associated system, we used Large Language Models (LLMs)
in the following capacities, in accordance with the journal's guidelines.

\paragraph{Experimental data generation.}
GPT-4o (OpenAI) was used to generate tags for the children's literature dataset.
Specifically, for each of the 409 books, GPT-4o produced soft genre assignments,
and noun/adjective tags that serve as input features to the
OT-FB learning pipeline.

\paragraph{Programming assistance.}
ChatGPT (OpenAI), Claude (Anthropic), and Cursor were used to assist in developing
the web application. Concretely, they supported code generation and debugging
for the TypeScript, React, and Node.js implementation of the multi-floor library interface.

\paragraph{Manuscript preparation.}
Claude (Anthropic) was used for translation assistance (converting the authors' ideas
from Japanese to English), language polishing (grammar, sentence structure, and clarity),
and consistency checking (terminology throughout the manuscript).

\paragraph{Human oversight.}
All scientific content---conceptual frameworks, mathematical formulations, experimental
designs, results, and interpretations---originated entirely from the authors.
All LLM outputs were critically reviewed, and the authors retain full responsibility
for all claims and content in this manuscript.


\section{Acknowledgments}
We are deeply grateful to the reviewers for their thorough and constructive feedback.
Their comments led us to substantially deepen our understanding of our own research,
and the paper has been greatly strengthened as a result.

This research was supported in part by JSPS KAKENHI Grant Number 21K12061 and 26K14941.
We also gratefully acknowledge the support of Zozo, Inc.
We are deeply grateful to Ms.\ Hirowatari for her invaluable assistance.
The music data used in this study was utilized in accordance with YouTube's terms of service,
based on content from YouTube Music.

\end{document}




